EDLD 651 Final Project Presentation

### 2020-12-04 presentation.Rmd
added paper draft and ref doc
added a word doc of the final paper draft and added a reference list doc

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mandy4.png" height="360" width="480">

@@

:::{}
 <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/cleaning.png" height="250" width="400">
:::

@@

:::{}
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/cloud5.png" height="225" width="300">
:::

@@

::: {}
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mountain2.png" height="200" width="300">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/purple.png" height="200" width="300">
:::

::: {}
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/veins2.png" height="200" width="300">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/tree2.png" height="200" width="300">
:::

::: {}
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/river3.png" height="200" width="300">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mud.png" height="200" width="300">
:::

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">

@@

<div class="col">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
</div>

<div class="col">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4nts3v.gif" height="300" width="400">
</div>

@@

## 
<!-- Ben -->
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group1.png" height = "600" width = "800">

##
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group2.png" height = "600" width = "800">

## 
<!-- Tess -->
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/0007.png" height="480" width="640">

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="480" width="640">

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/83QZ.gif" height="400" width="800">

>>>>

<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">

@@

:::{}
 <img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/cleaning.png" height="250" width="400">
:::

@@

:::{}
<!-- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/cloud5.png" height="225" width="300"> -->
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/cloud5.png" height="225" width="300">

:::

@@

::: {}
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mountain2.png" height="200" width="300">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/purple.png" height="200" width="300">
:::

::: {}
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/veins2.png" height="200" width="300">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/tree2.png" height="200" width="300">
:::

::: {}
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/river3.png" height="200" width="300">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mud.png" height="200" width="300">
:::

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">

@@

<div class="col">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
</div>

<div class="col">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4nts3v.gif" height="300" width="400">
</div>

@@

## 
<!-- Ben -->
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/group1.png" height = "600" width = "800">

##
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/group2.png" height = "600" width = "800">

## 
<!-- Tess -->
<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/0007.png" height="480" width="640">

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="480" width="640">

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/83QZ.gif" height="400" width="800">
